\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{tabularx}

% Title Configuration
\title{\textbf{StackStore: A Secure Distributed Runtime Environment for Uncompiled Source Code}}
\author{\textbf{Student Name: Shashwat Pratap Singh} \\ \textit{Department of Computer Science}}
\date{\today}

\begin{document}

\maketitle

\section{Abstract}
The modern software distribution model is fragmented. While Source Code Management (SCM) systems like GitHub host millions of open-source tools, the \textbf{Runtime Environment} required to execute them is often complex, platform-dependent, and prone to "Dependency Hell."

This project proposes \textbf{StackStore (Core Engine)}, a desktop runtime manager that utilizes OS-level virtualization to create ephemeral, isolated userspace environments on demand. By leveraging containerization technologies (Docker Engine), the system allows end-users to execute uncompiled source code (Python, Java, Node.js) directly from remote repositories without modifying the host operating system’s state.

\section{Motivation \& Future Integration}
The primary motivation for this project is to build the low-level \textbf{"Execution Engine"} for a larger, planned software ecosystem named \textbf{"StackStore"}.

While the future "StackStore" application will feature a Graphical User Interface (GUI), Cloud Offloading, and an AI-driven "App Store" experience, this semester project focuses strictly on the \textbf{Systems Engineering} challenges:
\begin{itemize}
    \item Designing the process orchestration layer.
    \item Implementing secure resource isolation.
    \item Managing the lifecycle of transient containers.
\end{itemize}
This "Core Engine" will serve as the backend infrastructure for the future full-stack application.

\section{Problem Statement}
\begin{enumerate}
    \item \textbf{Dependency Conflicts:} Installing multiple developer tools often leads to version mismatches (e.g., Python 3.8 vs 3.11) on the host OS, breaking existing workflows.
    \item \textbf{Security Vulnerabilities:} Executing arbitrary scripts from open-source repositories poses a significant risk to the host file system and kernel integrity.
    \item \textbf{Resource Leakage:} Short-term applications frequently leave behind residual files, registry keys, and background processes after uninstallation.
\end{enumerate}

\section{Proposed Architecture}
The system functions as an orchestration middleware between the Host Kernel and Remote Source Code.

\subsection{Core Mechanism: Containerization \& Isolation}
Instead of traditional installation, the application interacts with the \textbf{Docker Daemon} to spin up a micro-environment (Container) for every execution event.
\begin{itemize}
    \item \textbf{Namespace Isolation:} The application runs within its own Process ID (PID) namespace, preventing it from viewing or terminating host processes.
    \item \textbf{File System Virtualization:} The application interacts with a virtual root file system. All writes are Copy-on-Write (CoW) and are discarded instantly upon termination.
\end{itemize}

\subsection{Automated Environment Configuration}
To handle the diversity of build systems (Make, Gradle, NPM, Pip), the system integrates a deterministic parser to analyze the repository structure and generate a \textbf{Build Manifest}, automating the allocation of necessary libraries and binaries within the container.

\section{Alignment with Operating System Concepts}
This project is a practical implementation of key Operating System principles:

\begin{enumerate}
    \item \textbf{Process Management:} The backend acts as a hypervisor/supervisor, handling child process spawning (\texttt{fork/exec}), signal propagation (\texttt{SIGINT}, \texttt{SIGTERM}), and exit code analysis.
    \item \textbf{Resource Allocation:} The system defines strict CPU and Memory limits (via \texttt{cgroups}) for each container to prevent a single application from exhausting host resources (handling the "Noisy Neighbor" problem).
    \item \textbf{Inter-Process Communication (IPC):} The application streams \texttt{stdout} and \texttt{stderr} from the isolated container back to the host CLI via Unix Pipes or TCP Sockets for real-time user feedback.
\end{enumerate}

\section{Project Timeline (10 Weeks)}
The development lifecycle is adjusted to accommodate the academic calendar (including mid-semester examinations).

\begin{table}[h]
    \centering
    \begin{tabularx}{\textwidth}{|l|X|}
    \hline
    \textbf{Timeframe} & \textbf{Key Milestones \& Deliverables} \\
    \hline
    \textbf{Week 0} & \textbf{Mid-Semester Examinations} (No Project Activity) \\
    \hline
    \textbf{Weeks 1-3} & \textbf{Phase 1: Core OS Interface} \newline
    - Implementation of Node.js scripts to interface with Docker Daemon. \newline
    - Development of `child\_process` logic for container spawning and destruction. \newline
    - Implementation of Signal Handling for graceful shutdown. \\
    \hline
    \textbf{Weeks 4-6} & \textbf{Phase 2: Network \& File System} \newline
    - Integration of Git for secure repository cloning to temporary cache. \newline
    - Implementation of file system mounting (Host $\leftrightarrow$ Container) for input/output data persistence. \\
    \hline
    \textbf{Weeks 7-9} & \textbf{Phase 3: Integration \& CLI} \newline
    - Connecting the Network/Fetcher module with the OS Runner. \newline
    - Building a Command Line Interface (CLI) for user interaction and real-time log streaming (IPC). \\
    \hline
    \textbf{Week 10} & \textbf{Phase 4: Optimization \& Finalization} \newline
    - Performance testing (optimizing container startup latency). \newline
    - Final Report writing and Live Demonstration. \\
    \hline
    \end{tabularx}
    \caption{Implementation Schedule}
\end{table}

\section{Expected Outcome}
A functioning CLI prototype capable of:
\begin{enumerate}
    \item Cloning a remote repository via Git.
    \item Building a secure, isolated runtime environment based on the detected language.
    \item Executing the code and streaming Input/Output to the user interface.
    \item Performing a complete "Garbage Collection" of the environment post-execution.
\end{enumerate}

\end{document}